\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-03-21 paper/main.tex
comments

A developer needs to provide three scripts to integrate a fuzzing
tool: (1) a script that contains commands to run the tool; (2) a
preprocessing script to extract error types and buggy APIs for a
specific library version, and (3) a postprocessing script to match the
execution log with the expected errors needs to be provided. The
directory \CodeIn{tool-integration} that contains templates for these
scripts and their instantiations for FreeFuzz~\cite{wei2022free}, a
popular API fuzzer for DL libraries.
%
%% Tool execution proceeds in four steps: (1) Creation of Docker
%% container associated with a tool, (2) Reproduction of example bug from
%% the library version provided as input (3) Execution of preprocessing
%% script to extract error types and buggy APIs for a specific library
%% vesion (4) Execution of the tool and (5) Execution of postprocessing
%% script to match the execution log with the expected errors.

@@

The next four steps are executed with \tname's command
\CodeIn{run-tool}.

When the command is run, firstly an example bug that is reproducible with the library version provided as an input is run as a sanity check. Then, a preprocessing script to extract error types and buggy APIs for a specific library version runs.
Then the environment inside
the docker container of the tool is updated to match the library version passed as an input and the fuzzing tool runs inside the enviroment. After the execution is complete, the next step is running a postprocessing script that checks the execution log against the error types of the bug to determine if the bugs were reproduced or not.
For example, the following command runs FreeFuzz
on version 2.2.0 from \torch.

@@

% \Fix{Abid, this does not make sense to me. If you are checking this
%   manually, you could run FreeFuzz separately and check manually. What
%   is the point?! You need to provide a list of bugs and check
%   automatically how many the tool can find (based on some criteria,
%   e.g, match the error message in Assertion or some n frames in the
%   stack (for crash)). --Marcelo}
After the execution completes, the output can be
checked for all failures produced by FreeFuzz (saved inside the
container) and manually inspected to see if any failure that can
reveal the bug in question was generated by the tool. In this case,
the failure generated by FreeFuzz could not generate a failure that
can reveal this bug since the API "torch.\_dynamo.export" is not
supported by FreeFuzz.

>>>>

A developer needs to provide three scripts to integrate a fuzzing
tool: (1) a script that contains commands to run the tool; (2) a
preprocessing script to extract error types and buggy APIs for a
specific library version, and (3) a postprocessing script to match the
execution log with the expected errors needs to be provided.\Fix{name
  these scripts here and refer back to them in the text below} The
directory \CodeIn{tool-integration} that contains templates for these
scripts and their instantiations for FreeFuzz~\cite{wei2022free}, a
popular API fuzzer for DL libraries.

\Fix{remove this paragraph. Explain the steps when they appear. It is difficult
  to follow}
Tool execution proceeds in four steps: (1) Creation of Docker
container associated with a tool, (2) Reproduction of example bug from
the library version provided as input (3) Execution of preprocessing
script to extract error types and buggy APIs for a specific library
vesion (4) Execution of the tool and (5) Execution of postprocessing
script to match the execution log with the expected errors.\Fix{up to here}

@@

The next four steps are executed with \tname's command
\CodeIn{run-tool}.\Fix{I don't know what are the four steps (I can't
  remember anymore)}

\Fix{Can't you just explain what is the input-output and what it does
  (at a very high level)?}When the command is run, firstly an example bug that is reproducible with the library version provided as an input is run as a sanity check. Then, a preprocessing script to extract error types and buggy APIs for a specific library version runs.
Then the environment inside
the docker container of the tool is updated to match the library version passed as an input and the fuzzing tool runs inside the enviroment. After the execution is complete, the next step is running a postprocessing script that checks the execution log against the error types of the bug to determine if the bugs were reproduced or not.
For example, the following command runs FreeFuzz
on version 2.2.0 from \torch.

@@

% \Fix{Abid, this does not make sense to me. If you are checking this
%   manually, you could run FreeFuzz separately and check manually. What
%   is the point?! You need to provide a list of bugs and check
%   automatically how many the tool can find (based on some criteria,
%   e.g, match the error message in Assertion or some n frames in the
%   stack (for crash)). --Marcelo}
After the execution completes, the output can be
checked for all failures produced by FreeFuzz (saved inside the
container) and manually inspected to see if any failure that can
reveal the bug in question was generated by the tool. In this case,
the failure generated by FreeFuzz could not generate a failure that
can reveal this bug since the API "torch.\_dynamo.export" is not
supported by FreeFuzz.\Fix{This is bad in two way: (1) we did not give
  a chance to Freefuzz; unsupported API (2) it does not show any case
  where the tool can reproduce the bug (and demo that our matchers
  work). I hope you can do this on video or show another example to
  complement this or modify this.}
